% resume.tex
% 
% Credits to: 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%  
% To compile: 
% 	latex resume.tex
%	dvips -Ppdf -t letter resume.dvi
%	ps2pdf resume.ps resume.pdf

\documentclass[letterpaper,8pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\voffset}{-0.75in}
\setlength{\headsep}{35pt}
\setlength{\footskip}{11mm}


%-----------------------------------------------------------
\usepackage{shading}
\usepackage{setspace}
\usepackage[colorlinks = true,
            linkcolor = black,
            urlcolor  = black,
            citecolor = black,
            anchorcolor = black]{hyperref}
\usepackage{enumitem}

%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setstretch{1}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item[--] #1 \vspace{-1pt}}
\newcommand{\resheading}[1]{{\normalsize \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\vspace{0.1in}
\hspace{7mm}
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-4pt}}
%-----------------------------------------------------------


\begin{document}

\begin{center}
\textbf{\huge Arnav Nidumolu}
\end{center}
\begin{tabular*}{7in}{l@{\extracolsep{3.05in}}l}
\href{tel:9738455265}{(973)-845-5265}& \hfill \href{https://github.com/arnavn101}{github.com/arnavn101} \\
\href{mailto:arnav.nidumolu@gmail.com}{arnav.nidumolu@gmail.com} & \hfill \href{https://www.linkedin.com/in/arnav-nidumolu/}{linkedin.com/in/arnav-nidumolu} \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
	\ressubheading{University of Massachusetts Amherst}{Amherst, MA}{B.S. Computer Science (GPA 3.976)}{Graduation `24}
	\begin{itemize}[leftmargin=14mm, rightmargin=7mm]
		\resitem{Relevant courses: Distributed Computing, Reverse Engineering, Networking, Machine Learning}
	\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
Python, Java, C/C++, Rust, JavaScript/TypeScript, SQL
\item[Frameworks:]
Django, Flask, Scikit-learn, Pytorch, Keras, OpenCV, NLTK, Gensim, Celery
\item[Other Tools:]
AWS, Git, Docker, MongoDB, Github Actions, Redis, Bash Scripts
\end{description}

\resheading{Work Experience}

	\ressubheading{Amazon}{Seattle, WA}{Software Development Engineer}{Jul`24 - Current}
	\begin{itemize}[leftmargin=14mm, rightmargin=7mm]
		\resitem{Onboarded security tests to meet authn and authz standards for AWS Control Tower APIs.}
		\resitem{Curated Athena queries and configured Lakeformation permissions for AWS Glue ETL workflows.}
	\end{itemize}

	\ressubheading{Amazon}{Seattle, WA}{Software Dev Engineer Intern}{Jun`23 - Aug`23}
	\begin{itemize}[leftmargin=14mm, rightmargin=7mm]
		\resitem{Improved concurrency limitations of AWS Control Tower control operations by 2.5x.}
		\resitem{Implemented distributed queueing mechanism with scalability and fault tolerance.}
		\resitem{Created load and integration tests to evaluate concurrency limits and response times.}
	\end{itemize}

	\ressubheading{AuCode}{Amherst, MA}{Software Enginner Intern}{Jun`22 - Aug`22}
	\begin{itemize}[leftmargin=14mm, rightmargin=7mm]
		\resitem{Streamlined DevOps workflow with Github actions, Amazon ECS, and Application load balancers.}
		% \resitem{Developed web crawling infrastructure with autoscaling capabilities using Redis message queues and Celery workers.}
		% \resitem{Automated migration from RDS PostgreSQL to Amazon S3 in parquet format.}
		\resitem{Utilized Gensim/GPT3/Sklearn to train models for topic-modeling and NLP classification tasks.}
	\end{itemize}

	\ressubheading{Red Hat}{Boston, MA}{Research Intern for ChRIS Project}{Jun`20 - Aug`20}
	\begin{itemize}[leftmargin=14mm, rightmargin=7mm]
		\resitem{Designed monitors with Jenkins to measure system performance and take corrective actions.}
		% \resitem{Enabled faster runtime for Image detection Proof of Concept with GPU capabilities of Tensorflow.}
		\resitem{Ensured scalable/reliable services by optimizing multithreading and identifying deadlock scenarios.}
	\end{itemize}


\resheading{Hackathons \& Projects}

	\ressubheading{Agora}{May `24}{}{\href{https://github.com/CS520-news-aggregator/agora}{github.com/CS520-news-aggregator/agora}}
	\begin{itemize}[leftmargin=14mm, rightmargin=7mm]
		\resitem{Leverages Google's Gemma LLM to provide users with news posts based on their preferences.}
	\end{itemize}

	% \ressubheading{Quantify}{Mar `22}{}{\href{https://github.com/GreenPlanet-Capital/Quantify}{github.com/GreenPlanet-Capital/Quantify}}
	% \begin{itemize}[leftmargin=14mm, rightmargin=7mm]
	% 	\resitem{Performs technical analysis and backtesting for financial assets with Alpaca API integration.}
	% \end{itemize}

	\ressubheading{UMass UnBoxed}{HackUMass `23}{Awarded Best Web Hack}{\href{https://devpost.com/software/umass-unboxed}{devpost.com/software/umass-unboxed}}
	\begin{itemize}[leftmargin=14mm, rightmargin=7mm]
		\resitem{Full-Stack platform built on Svelte, Django, and MongoDB for buying and selling goods on campus.}
	\end{itemize}

	\ressubheading{Smart Notes}{HackPHS `19}{Awarded Best Cloud Hack}{\href{https://devpost.com/software/smart-notes}{devpost.com/software/smart-notes}}
	\begin{itemize}[leftmargin=14mm, rightmargin=7mm]
		\resitem{Creates concise summary of a website, video, or document using Google's Page Rank algorithm.}
	\end{itemize}

\end{document}
